\documentclass[11pt,a4paper,sans,english]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage{fontspec}

\usepackage[margin=1.0cm,a4paper,ignoreall]{geometry}
\usepackage{babel}

% personal data
% Put your private data in a file named "personal-data.tex".
\IfFileExists{personal-data.tex}{
    \input{personal-data}
}{
    \name{Chih-Yung Liang}{\fontspec{msjh}(梁智湧)}
    \phone[mobile]{+886 9??-???-???}
    \address{No. 1, Sec. 4, Roosevelt Rd., Taipei 10617, Taiwan}
    \email{cyliang@users.noreply.github.com}
    \social[linkedin]{chihyung-liang}
    \social[github]{cyliang}
}

\begin{document}

\hypersetup{
    pdfauthor={Chih-Yung~Liang},
    pdftitle={Chih-Yung~Liang's Resum\'{e}},
    pdfsubject={Resum\'{e} of Chih-Yung~Liang},
    pdfkeywords={Chih-Yung~Liang, resum\'{e}},
}

\makecvtitle

\section{Education}
    \cventry
        {2016--Present} % year
        {MSc student in Computer Science} % degree
        {National Taiwan University} % institute
        {Taipei, Taiwan} % city
        {Institute of Networking and Multimedia} % description
        {\cvlistdoubleitem{Advisor: Prof. Wei-Chung Hsu}{Overall: GPA 4.24/4.3, class rank 3/40}}

    \cventry
        {2012--2016}
        {BSc in Computer Science}
        {National Chiao Tung University}
        {Hsinchu, Taiwan}
        {Department of Computer Science}
        {\cvlistitem{Won \underline{5 academic achievement awards} (top 5\% of class in semester), Fall 2013--Fall 2015}%
        \cvlistdoubleitem{Last 60 credits: GPA 4.06/4.3}{Overall: GPA 3.89/4.3, class rank 3/54}}
        
\section{Publication (accepted)}
    \begin{itemize}
    \item C. Liang, S. Fu, Y. Liu and W. Hsu, "Automatically Migrating Sequential Applications to Heterogeneous System Architecture", in \textit{The 2018 International Conference on High Performance Computing \& Simulation, Special Session on Compiler Architecture, Design and Optimization}, Orléans, France, Jul. 2018. (URL: \href{https://goo.gl/Cf8Azp}{https://goo.gl/Cf8Azp})
        \begin{itemize}
        \item \textbf{Description}: \textit{Heterogeneous System Architecture (HSA)} is a hardware architecture for more efficient heterogeneous computing. Built on \textit{LLVM}, our framework transforms sequential code and generates GPU binary with LLVM's backends. It includes polyhedral dependence checking and a runtime dispatching scheduler. On an AMD's HSA-compliant machine, a sequential application running through this framework could be 8.66x faster than before.
        \end{itemize}
    \end{itemize}
    
\vspace{-5pt}
\section{Experience}
    \cventry
        {Sept. 2017--Jan. 2018} % period
        {Intern} % job title
        {Industrial Technology Research Institute (ITRI)} % employer
        {Hsinchu, Taiwan} % city
        {Information and Communications Research Laboratories} % department
        {\cvlistitem{Surveyed Control Flow Integrity and helped decide team's project direction}} % short description

    \cventry
        {July 2016--Aug. 2016}
        {Intern}
        {Industrial Technology Research Institute (ITRI)}
        {Hsinchu, Taiwan}
        {Service Systems Technology Center}
        {\cvlistitem{Built a system for electronic commerce and social media analysis}}
        
    \cventry
        {Apr. 2015--Oct. 2015}
        {Part-time assistant}
        {National Chiao Tung University}
        {Hsinchu, Taiwan}
        {Information Technology Service Center}
        {\begin{itemize}
        \item Penetration testing for 26 school's internal website systems
        \item Found and reported 20 security issues leaking personal information in 13 systems
        \end{itemize}}
        
\section{Skills}
    \cvlistdoubleitem{\textbf{Compiler Optimization (LLVM)}}{Computer Security}
    \cvlistdoubleitem{\textbf{Heterogeneous System Architecture (HSA)}}{Web and iOS Development}
    \cvlistitem{Programming Languages: C/C++ > Python > Swift > C\# = PHP = JavaScript}
        
\section{Projects and Scholarships}
    \cventry
        {2014--2016} % period
        {An automatic framework capable of various exploitation in penetration testing} % description
        {Modulized APT Framework for Red Team Practice} % title
        {}
        {} % link
        {\cvlistdoubleitem{Advisor: Prof. Shiuhpyng Shieh}{Won \underline{3 bachelor's project scholarships}}%
        \cvlistitem{Won \underline{College Student Research Scholarship}, Ministry of Science and Technology, Taiwan, July 2015--Fab. 2016}}
        
    \cventry
        {2015}
        {Accelerate application "Find Face" with a FPGA Intellectual Property}
        {Hardware-software Co-design for Accelerating Sequential Image Pattern Searching Application}
        {}
        {\href{https://github.com/cyliang/shlab-final}{\textnormal{https://github.com/cyliang/shlab-final}}}
        {\begin{itemize}
        \item Advisor: Prof. Chun-Jen Tsai
        \item Won \underline{The Yin Zhi Tong Memorial Scholarship}, 2016 (2--3 grants per year)
        \end{itemize}%
        }

%    \cventry
%        {2016}
%        {A virtual reality environment with HTC Vive for programming or working}
%        {FIVE: Five Is VR Editor}
%        {}
%        {\href{https://github.com/cyliang/FIVE}{\textnormal{https://github.com/cyliang/FIVE}}}
%        {}
        
%    \cventry
%        {2014}
%        {A website case for sport event registration}
%        {Registration Website for Office of Physical Education, National Chiao Tung University}
%        {}
%        {\href{http://140.113.104.243/sport/}{\textnormal{http://140.113.104.243/sport/}}}
%        {\cvlistitem{Capable of coping with instantaneous peak flow of hundreds of people}}
        
\section{Certificate}
    \cventry
        {Oct. 2015} % time
        {Professional} % level
        {Collegiate Programming Examination, ACM-ICPC Contest Council for Taiwan} % title
        {}
        {rank 1.5\%} % grade
        {}

%\clearpage
%%-----       letter       ---------------------------------------------------------
%% recipient data
%\recipient{}{\\\\}%<Company Recruitment team%:columnShift:-7,persistent%>%<Company's name%:columnShift:-5,persistent%>%<Street address%:columnShift:-3,persistent%>%<Zip Code City%:columnShift:-1,persistent%>
%\date{}%<Date%:columnShift:-1,persistent%>
%\opening{}%<Dear Sir or Madam,%:columnShift:-1,persistent%>
%\closing{}%<Yours faithfully,%:columnShift:-1,persistent%>
%\enclosure{}%<enclosures%:columnShift:-1,persistent%>          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle
%\makeletterclosing
\end{document}